The Emperor Has No Clothes

### 2012-03-30 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@6694 ac11df5e-a788-c23b-a8e1-c758c323924d

Before concluding, we comment on two scenarios that may explain the
observed \lya\ emission for LBGs.  Regarding the \lya\ kinematics, we
have emphasized that the observed velocity shift demands a high
opacity gas to force photon diffusion in frequency space.  Following
\cite{neufeld91}, a static slab of gas with optical depth $\tau_0 >
10^X$ and $b \approx 10 \mkms$ (i.e.\ $\mnhi > 10^{X} \cm{-2}$) would
produce significant line-emission at $\Delta v \gtrsim +400 \mkms$.

In contrast to our assertions,
other authors have modeled the \lya\ profiles of LBGs and have
concluded the redshifted emission is a `clear signature' of an
outflow.
The [most extensive] modeling of \lya\ emissoin by LBGas to date has
been performed by A. Verhomme and collaborators
\citep{verhommea,verhommeb}.  Their preferred model has been a thin
expanding shell characterized by the expansion speed $v_{\rm exp}$ and
total surface density of \ion{H}{1} gas in the shell.  Although the
shell's dynamics play a role in the \lya\ emission kinematics, the
[dominant] aspect for the emergent spectrum is the \ion{H}{1} column
density.  Indeed, they only predict a dominant emission peak at $v \gg
0 \mkms$ if $\mnhi > 2\sci{20} \cm{-2}$.  For lower values, the
emission is preferentially at $v \lesssim +100 \mkms$.  The
explanation is similar to the ISM model described above;  large \nhi\
values force diffusion of \lya\ in frequency.  Furthermore, their
models predict substantial \lya\ absorption at $v < 0 \mkms$.  
Strong absorption is observed in a handful of individual spectra
\citep[e.g.][]{cb58,dessauges}, but is not evident in the stacked
spectra of \cite{shapley93} or \cite{steidel+10}.  
[Why is there sometimes weak \lya\ emission at $v < 0 \mkms$ in LAEs
at $z \sim 3$?]
[Redshfited, asymmetric emission is suggestive of an outflow]

>>>>

Before concluding, we comment on two scenarios that may explain the
observed \lya\ emission for LBGs.  Regarding the \lya\ kinematics, we
have emphasized that the observed velocity shift demands a high
opacity gas to force photon diffusion in frequency space.  Following
\cite{neufeld91}, a static slab of gas with optical depth $\tau_0 >
10^7$ and $b \approx 10 \mkms$ (i.e.\ $\mnhi > 5\sci{20} \cm{-2}$) would
produce significant line-emission at $\Delta v \gtrsim +400 \mkms$.  
Such column densities are characteristics of the Galactic ISM and are
frequently observed as so-called damped \lya\ systems in the spectra
of background quasars and gamma-ray burst (GRB) afterglows
\citep[e.g.][]{phw05,wgp05,pcd+08}.   Indeed, if GRBs trace
representative star-forming regions of high-$z$ galaxies, one
regularly observes \ion{H}{1} gas with $\tau_0 > 10^7$ \citep{otherguy,pcd+08}.

In this ISM scenario, \lya\ emission will occur at both positive and
negative velocities relative to systemic.  For LBGs, however, one
generally observes only emission at $\Delta v \gg 0 \mkms$.  
One would therefore require the outflow to significantly absorb the
blue peak of \lya\ emission.  This implies two important predictions: 
(i) the system has very high opacity to \lya\ at $v \approx 0 \mkms$,
i.e.\ one expects a DLA absorption profile;
(ii) an LBG outflow with low opacity should whow \lya\ emission at
$\Delta v < 0 \mkms$.  On the latter point, \cite{erb+10} recently
reported on an LBG with weak low-ion absorption that also shows
significantly \lya\ emission at positive velocities.  [But no DLA!!]
Similarly, \cite{heckman+11} have published several examples of
star-forming systems at low-$z$ that have weak low-ion absorption in
their outflows and also significant blue-shifted \lya\ emission.  
[COMMENT ON DLA NOW]

[Consider the effects of spectral resolution on \lya\ + DLA]

An alternative model (which need not be entirely distinct) is to
locate the high opacity \ion{H}{1} gas within the outflow.  This is
the principal feature of the expanding shell models of
A. Verhomme and collaborators \citep{verhommea,verhommeb}.  
Their preferred model has been a thin
expanding shell characterized by the expansion speed $v_{\rm exp}$ and
total surface density of \ion{H}{1} gas in the shell.  Although the
shell's dynamics play a role in the \lya\ emission kinematics, the
[dominant] aspect for the emergent spectrum is the \ion{H}{1} column
density.  Indeed, they only predict a dominant emission peak at $v \gg
0 \mkms$ if $\mnhi > 2\sci{20} \cm{-2}$.  For lower values, the
emission is preferentially at $v \lesssim +100 \mkms$.  The
explanation is similar to the ISM model described above;  large \nhi\
values force diffusion of \lya\ in frequency.  Furthermore, their
models predict substantial \lya\ absorption at $v < 0 \mkms$.  
Strong absorption is observed in a handful of individual spectra
\citep[e.g.][]{cb58,dessauges}, but is not evident in the stacked
spectra of \cite{shapley93} or \cite{steidel+10}.  
[FOLLOW THE WEAK METALS, e.g. 1808]

Neither of the models proposed above are likely to yield significant
spatially-extended \lya\ emission.  In fact, we consider it very
difficult ot construct a clumpy or diffuse medium model that would
reproduce the observed surface brightness profile of S+11.  We suspect
instead that the diffuse emission is generated by sources (e.g.\
satellite galaxies) that surround the LBG.  Indeed, \cite{kasen+11}
predict from cosmological simulations of star-forming galaxies very
similar average emission profiles from XXX.

[FINISH WITH A BRIEF DISCUSSION ON IMPLICATIONS FOR THE CLUMP OUTFLOW]
